CommonMind Consortium: DLPFC

### 2020-10-13 combined_analysis/CTS/GABA.Rmd
drop genes that don't vary

  idx = METADATA$Cohort == chrt

  # get variance withing cohort
  # only keep genes with variance > 0
  v = apply( geneExpr[,idx], 1, var)

  E = geneExpr[v > 0,idx]

@@

# Sex by Disease interaction
```{r dream.sex.disease}
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx*Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
  `NIMH-HBCC`       = ~ Dx*Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

@@

# Dx test separately in Males and then Females
```{r dream.sex.disease.separately}
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
  `NIMH-HBCC`       = ~ Dx + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

>>>>

  # get variance within cohort and sex
  # only keep genes with variance > 0
  # v = apply( geneExpr[,idx], 1, var)
  v = lapply( unique(METADATA$Reported_Gender), function(Gnd){
    idx = with(METADATA, (Cohort == chrt) & (Reported_Gender==Gnd))
    isVar = apply( geneExpr[,idx], 1, var) > 0
    names(isVar[isVar])
    })

  # genes with variance in both sexes
  isexpr = intersect(v[[1]], v[[2]])

  # get expressed genes form this cohort
  E = geneExpr[isexpr, METADATA$Cohort == chrt]

@@

# Sex by Disease interaction
```{r dream.sex.disease}
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx*Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*ageOfDeath ,
  `NIMH-HBCC`       = ~ Dx*Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath )

@@

# Dx test separately in Males and then Females
```{r dream.sex.disease.separately}
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*ageOfDeath ,
  `NIMH-HBCC`       = ~ Dx + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath)

### 2020-10-13 combined_analysis/CTS/Glu.Rmd
test
drop genes that don't vary

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: Glu',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

thisFileName <- paste0(params$cellType, '.Rmd')

@@

```{r store, eval=TRUE}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = gsub(":", " -",activityName), parentId = parentId)
  CODE <- synStore(CODE)

>>>>

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: GABA',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

thisFileName <- paste0(ifelse(params$cellType=='GLU', 'Glu', 'GLU'), '.Rmd')

@@

```{r store, eval=TRUE}

if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = gsub(":", " -",activityName), parentId = parentId)
  CODE <- synStore(CODE)

### 2020-10-13 combined_analysis/CTS/MgAs.Rmd
drop genes that don't vary

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "MgAs"
---

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: MgAs',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

v = apply(geneExpr, 1, var)

@@

    # Compute residuals which adding back Diagnosis and Sex effects
    resid.lst = fitVarPartModel(vobj, form_use, info, fxn = f, BPPARAM = SnowParam(4))  
    do.call(rbind, resid.lst)
    })
  names(residuals.lst) = names(vobj.lst)

@@

  fit = dream(vobj[keep.ensID,], form_use, info, BPPARAM = SnowParam(4))  
  eBayes( fit )
  })
names(fit_inter_sex.disease.lst) = names(vobj.lst)

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: TRUE
  cellType: "MgAs"
---

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: GABA',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

@@

    # Compute residuals which adding back Diagnosis and Sex effects
    resid.lst = fitVarPartModel(vobj, form_use, info, fxn = f, BPPARAM = SnowParam(18))  
    do.call(rbind, resid.lst)
    })
  names(residuals.lst) = names(vobj.lst)

@@

  fit = dream(vobj[keep.ensID,], form_use, info, BPPARAM = SnowParam(18))  
  eBayes( fit )
  })
names(fit_inter_sex.disease.lst) = names(vobj.lst)

### 2020-10-13 combined_analysis/CTS/Olig.Rmd
drop genes that don't vary

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "Olig"
---

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: Olig',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: TRUE
  cellType: "Olig"
---

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: GABA',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```
